Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?

### 2018-09-18 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Add Victoria to scraper

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We then examine the effect of various events using a discrete choice model. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard and then one of Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government. However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.

In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days and changes over time, and for dimension reduction. We then use a discrete choice model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).

@@

# Model
The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage. The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent. In this section a brief overview of both the LDA model and the STM approach is provided and then the specifics of how we consider events in this setting are discussed.

>>>>

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to categorise what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We then examine the effect of various events using a discrete choice model. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results are dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant and persistent effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal predecessor Kevin Rudd's carbon tax. Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government. However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.

In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 for dimensionality reduction and to impose structure such as correlation between days and changes over time. We then use a discrete choice model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).

@@

# Model
The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage. The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent. In this section a brief overview of both the LDA model and the STM approach is provided. In a similar way to @MuellerRauh2018 we consider the outputs of the topic model as reduced dimension inputs. In our case they are inputs to a discrete choice model, and so we then discuss that model.
